---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

`smargins` is a package that aids in calculating Average Marginal
Effects for models of various kinds. There are many packages like it
(e.g., [coreSim](https://cran.r-project.org/web/packages/coreSim/),
[effects](https://cran.rstudio.com/web/packages/effects/),
[lsmeans](https://cran.rstudio.com/web/packages/lsmeans/),
[margins](https://cran.rstudio.com/web/packages/margins/),
[rms](https://cran.rstudio.com/web/packages/rms/) and
[Zelig](https://cran.rstudio.com/web/packages/Zelig/)) but this one is
mine.

The main functions provided by this package are:
* `smargins()` calculates average marginal effects
* `scompare()` performs pairwise comparisons of the average marginal effects produced by `smargins`.

Some examples are available at (https://izahn.github.io/smargins/)

## Purpose

The primary purpose of this package is to serve as a test bed for exploring interfaces and designs for R packages that facilitate calculating quantities of interest. Several such packages exist, each with their own pros and cons. This package is serves as a play ground where we can try different approaches in order to see if we can find one with more pros and fewer cons than existing solutions.

## Installation

`smargins` is not on CRAN (and may never be). You can install it from github using the `devtools` package:

```{r, eval=FALSE}
## install.packages("devtools")
devtools::install_github("izahn/smargins")
```

## Usage

```{r}
library(smargins)

mtc <- transform(mtcars, gear = factor(gear))

m.sm <- smargins(lm(mpg ~ gear, data = mtc),
                 gear = levels(gear))
summary(m.sm)

summary(scompare(m.sm, "gear"))

```

