---
title: "smargins Questions and Discussion"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
        stop_on_error = 2L
)
```

# Specify x variable names or values?

```{r, echo = FALSE}
library(smargins)
```

Given the following model:

```{r}
m <- lm(mpg ~ hp + wt + gear, data = mtcars)
```

suppose that we wish to examine the effect of `hp` by calculating expected values at several levels of `hp` while averaging over the observed values of `wt` and `gear`.

Which do you like better?

```{r}
smargins_v1(m, hp = quantile(hp))
```

or

```{r}
smargins_v2(m, "hp")
```

?

Now suppose that we want to choose the values of hp ourselves:

```{r}
smargins_v1(m, hp = seq(50, 350, by = 50))
```

or

```{r}
smargins_v2(m, "hp", xvalues = list(hp = seq(50, 350, by = 50)))
```

Now which do you prefer? 

`smargins_v1` is more verbose for the simple case, but less so when the user does wish to specify values. Which one should we pick? Or is there some combination or alternative that would be even better?

# Interface for comparisons

Currently there is a `scompare` function that calculates pairwise differences for each combination of values on a particular predictor variable. For example, we can compare the differences between expected values for each level of `gear` as follows:
```{r}
summary(scompare(smargins(m, gear = sort(unique(gear))), var="gear"))
```

It would be nice to offer some flexibility here so that comparisons other than pairwise can be made. There are a few different interfaces we might choose from.

Some options include:

- matrix based, like `car::lht`, and https://github.com/goshevs/effcomp
- character representation, like `car::lht`
- function based, like `emmeans::contrast`
- function based, but function does computation directly

A few examples follow below.

## Matrix interface for comparisons

```{R}
summary(scompare_v1(smargins(m,
                             gear = sort(unique(gear))),
                    var = "gear",
                    contrast = c(-1, 0, 1)))
```

```{R}
summary(scompare_v1(smargins(m,
                             gear = sort(unique(gear))),
                    var = "gear",
                    contrast = c(-0.5, -0.5, 1.0)))
```


## Simple function based interface to comparisons


```{R}
summary(scompare_v2(smargins(m,
                             gear = sort(unique(gear))),
                    var = "gear",
                    contrast.fun = function(a, b, c) a - b + 0*c))
```

Naming is a problem...

```{R}
summary(scompare_v2b(smargins(m,
                             gear = sort(unique(gear))),
                    var = "gear",
                    contrast.funs = list("3 vs 4" = function(a, b, c) a - b + 0*c)))
```

```{R}
summary(scompare_v2b(smargins(m,
                             gear = sort(unique(gear))),
                    var = "gear",
                    contrast.funs = list("3 and 4 vs 5" = function(a, b, c) .5*a + .5*b + - c)))
```


After looking at these examples I'm not sure we have a clear winner yet. Perhaps there is another way that I haven't thought of yet? If you think of one please let me know by opening an issue at https://github.com/izahn/smargins/issues
