---
title: "smargins Quickstart Guide"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quickstart Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
        stop_on_error = 2L
)
```

## Workflow overview

Models in R can generally be fit using a formula interface. The fitted
models can then be explored and post-processed in various was, for
example to display an ANOVA-style table, calculate confidence
intervals, or plot predictions from the model. This package provides
additional post-estimation functions to calculate average marginal
effects along with simulation-based estimates of uncertainty.

# Examples

Let’s walk through an example. This example uses the Prestige dataset.
It contains data on 102 occupations. We will model the effect of
education and type on income.

## Building Models

Since income is a continuous variable, least squares is an appropriate
model choice. To estimate our model, we call the `lm` function:

```{r}
# load data
options(StringsAsFactors = FALSE)
data(Prestige, package = "car")

Prestige <- na.omit(Prestige)

# estimate ls model
m1 <- lm(income ~ education + type, data = Prestige)

# model summary
summary(m1)
```

Since this is an ordinary least squares regression, the coefficients
are themselves quantities of interest. The `education` coefficient tells
us that (holding occupation type constant) every additional year of
education is associated with an \$887.9 increase in income. The coefficients for `typeprof` and `typewc` are slightly more difficult to interpret. They are dummy codes that tell us the expected difference between blue-collar and professional incomes, and between blue-collar and white-collar incomes.

Although the model coefficients are not difficult to interpret, the
average marginal effects are even more straight-forward. We can
calculate theme using the `smargins` function.
  
```{r}
library(smargins)

ppred1 <- smargins(m1, at = list(type = unique(Prestige$type)))

ppred1
```

The print method shows us how the result is organized. There is a
summary method that gives a default set of statistics for each
combination of values specified in the `at` argument:

```{r}
summary(ppred1)
```


## Comparisons
The summary method shows expected values for each value specified in
the `at` argument, but frequently we want some transformation of these
values. There is a `scompare` function that gives pairwise
differences:

```{r}
summary(scompare(ppred1, "type"))
```

but the really great thing is that the structure is simple enough that the user can perform their own arbitrary transformations. For example, we can compare the average of white collar and professional with blue collar:

```{r}
bc <- subset(ppred1, type == "bc")$.smargin_qi
wc_prof <- subset(ppred1, type == "wc")$.smargin_qi +
           subset(ppred1, type == "wc")$.smargin_qi
sumstats(bc - wc_prof)
```

## Visualizations

Another advantage of the simple data structure returned by `smargins` is that it makes creating plots using standard graphics packages in R easy. For example, we can graph the expected values by type:

```{r}
library(ggplot2)

ggplot(summary(ppred1),
       aes(x = mean, y = type)) +
    geom_point() +
    geom_errorbarh(aes(xmin = lower_2.5, xmax = upper_97.5),
                   height = 0.25)
```

```{r}
ggplot(ppred1,
       aes(x = .smargin_qi)) +
    geom_density(aes(fill = type), alpha = 0.25)
```

This is especially useful for plotting interactions:

```{r}
m2 <- lm(income ~ education*type, data = Prestige)

m2.sm <- smargins(m2, at = list(education = 6:16, type = c("bc", "prof", "wc")))

ggplot(summary(m2.sm),
       aes(x = education, y = mean, color = type)) +
    geom_smooth(aes(ymin = lower_2.5, ymax = upper_97.5),
                stat = "identity",
                alpha = 0.25) + facet_wrap(~type)
```
