---
title: "Expected Values for LMs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AMEs for GLMs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
        stop_on_error = 2L
)
knitr::opts_chunk$set(
    fig.height = 11,
    fig.width = 7
)
```

## Examples

### Simple first differences

Load Zelig and attach example data frame:

```{r}
data(macro, package = "Zelig")
```

Estimate model:

```{r message=FALSE}
m1 <- lm(unem ~ gdp + capmob + trade, data = macro)
```

Summarize regression coefficients:

```{r, eval = TRUE}
summary(m1)
```

Set explanatory variables to their default (mean/mode) values, with
high (80th percentile) and low (20th percentile) values for the trade
variable:

```{r, eval = TRUE}
library(smargins)
m1.sm <- smargins(m1, trade = quantile(trade, c(0.2, 0.8)))
summary(m1.sm)
```

Calculate first differences for the effect of high versus low trade on GDP:

```{r, eval = TRUE}
summary(scompare(m1.sm, var = "trade"))
```

Plot the simulated distributions:

```{r}
library(ggplot2)

ggplot(m1.sm, aes(x = .smargin_qi, fill = factor(trade))) +
    geom_density(alpha = 0.25)

ggplot(scompare(m1.sm, var = "trade"), aes(x = .smargin_qi, fill = factor(trade))) +
    geom_density()
```

### Categorical variables, including fixed effects

Estimate a model with fixed effects for each country.

```{r}
m2 <- lm(unem ~ gdp + trade + capmob + country, data = macro)
```

Calculate expected values for each country.

```{r}
m2.sm <- smargins(m2, country = unique(country))

summary(m2.sm)

(m2.sm.comp <- summary(scompare(m2.sm, var = "country")))
```

Plot.

```{r}
m2.sm.comp$country <- reorder(m2.sm.comp$country, m2.sm.comp$median)

ggplot(m2.sm.comp, aes(y = country, x = median)) +
    geom_point() +
    geom_errorbarh(aes(xmin = lower_2.5, xmax = upper_97.5), height = .2)
```
