---
title: "Expected Values for GLMs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AMEs for GLMs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
        stop_on_error = 2L
)
knitr::opts_chunk$set(
    fig.height = 11,
    fig.width = 7
)
```

## Examples

### Basic example

Attach the sample turnout dataset:

```{r}
data(turnout, package = "Zelig")
```

Estimating parameter values for the logistic regression:

```{r}
m1 <- glm(vote ~ age + race, family = binomial(link = "logit"), data = turnout)
```

Summarize estimated parameters:

```{r}
summary(m1)
```

For `logit` models you may wish to calculate odds ratios:

```{r}
cbind(OR = exp(coef(m1)), exp(confint(m1)))
```

Set values for the explanatory variables and simulate quantities of
interest from the posterior distribution:

```{r}
library(smargins)
m.sm <- smargins(m1, age = 36, race = "white")
summary(m.sm)
```

Show the results graphically:

```{r}
library(ggplot2)

ggplot(m.sm, aes(x = .smargin_qi)) +
    geom_density(aes(fill = interaction(age, race)))
```

## First differences

Estimating the risk difference (and risk ratio) between low education (25th
percentile) and high education (75th percentile) while all the other variables
averaged over their observed values.

```{r}
m2 <- glm(vote ~ educate, data = turnout, family = binomial(link = "logit"))
m2.sm <- smargins(m2, educate = quantile(educate, prob = c(0.25, 0.75)))

summary(m2.sm)
summary(scompare(m2.sm, var = "educate"))
```

```{r}
ggplot(scompare(m2.sm, "educate")) +
    geom_density(aes(x = .smargin_qi, fill = factor(educate)))

ggplot(m2.sm, aes(x = .smargin_qi)) +
    geom_density(aes(fill = factor(educate)))
```

## Model Definition

Let $Y_i$ be the binary dependent variable for observation $i$ which takes the
value of either 0 or 1.

- The *stochastic component* is given by

$$\begin{aligned}
Y_i &\sim& \textrm{Bernoulli}(y_i \mid \pi_i) \\
    &=& \pi_i^{y_i} (1-\pi_i)^{1-y_i}\end{aligned}
$$

where $\pi_i=\Pr(Y_i=1)$.

- The *systematic component* is given by:

$$\pi_i \; = \; \frac{1}{1 + \exp(-x_i \beta)}.$$

where $x_i$ is the vector of $k$ explanatory variables for observation $i$
and $\beta$ is the vector of coefficients.

## Quantities of Interest

- The expected values for the logit model are simulations of the predicted probability of a success:

$$
E(Y) =
  \pi_i= \frac{1}{1 + \exp(-x_i \beta)},
$$

given draws of $\beta$ from its sampling distribution.

- The predicted values are draws from the Binomial distribution with mean equal to the simulated expected value $\pi_i$.

- The first difference for the logit model is defined as

$$\textrm{FD} = \Pr(Y = 1 \mid x_1) - \Pr(Y = 1 \mid x).$$

The risk ratio is defined as

$$\textrm{RR} = \Pr(Y = 1 \mid x_1) \ / \ \Pr(Y = 1 \mid x).$$

In conditional prediction models, the average expected treatment effect (att.ev) for the treatment group is

$$
\frac{1}{\sum_{i=1}^n t_i}\sum_{i:t_i=1}^n \left\{ Y_i(t_i=1) -
      E[Y_i(t_i=0)] \right\},
$$

where $t_i$ is a binary explanatory variable defining the treatment ($t_i=1$) and control ($t_i=0$) groups.
Variation in the simulations are due to uncertainty in simulating $E[Y_i(t_i=0)]$, the counterfactual
expected value of $Y_i$ for observations in the treatment group, under the assumption that everything
stays the same except that the treatment indicator is switched to $t_i=0$.

- In conditional prediction models, the average predicted treatment effect (att.pr) for the treatment group is

$$
\frac{1}{\sum_{i=1}^n t_i}\sum_{i:t_i=1}^n \left\{ Y_i(t_i=1) -
      \widehat{Y_i(t_i=0)}\right\},
$$

where $t_i$ is a binary explanatory variable defining the treatment ($t_i=1$) and control ($t_i=0$) groups. Variation in the simulations are due to uncertainty in simulating $\widehat{Y_i(t_i=0)}$, the counterfactual predicted value of $Y_i$ for observations in the treatment group, under the assumption that everything stays the same except that the treatment indicator is switched to $t_i=0$.
