---
title: "Expected Values for Regression with Survey Weights"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ame-survey-glm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
    stop_on_error = 2L
)
knitr::opts_chunk$set(
    fig.height = 11,
    fig.width = 7
)

options(cite = FALSE)
```
---

Logit Regression for Dichotomous Dependent Variables with Survey Weights with
`logit.survey`.

Use logit regression to model binary dependent variables specified as a
function of a set of explanatory variables.

Examples
------

```{r, eval = TRUE, echo = FALSE}
rm(list=ls(pattern="\\.out"))
suppressWarnings(suppressMessages(library(Zelig)))
set.seed(1234)
```

### Example 1: User has Existing Sample Weights

Our example dataset comes from the survey package:

```{r, eval = TRUE}
data(api, package = "survey")
```

In this example, we will estimate a model using
the percentages of students who receive subsidized
lunch and the percentage who are new to a school
to predict whether each California public school
attends classes year round.  We first make a numeric
version of the variable in the example dataset, which
you may not need to do in another dataset.

```{r, eval = TRUE}
library(survey)
apistrat.design <- svydesign(ids = ~1, weights = ~pw, data = apistrat)

m1 <- svyglm(yr.rnd ~ meals + mobility,
             design = apistrat.design,
             family = quasibinomial())

summary(m1)
```

Set explanatory variables to their observed values, and set
a high (80th percentile) and low (20th percentile) value for "meals,"
the percentage of students who receive subsidized meals:

```{r, eval = TRUE}
library(smargins)

m.sm1 <- smargins(m1, meals = quantile(meals, c(0.2, 0.8)))
summary(m.sm1)
```

Generate first differences for the effect of high versus low "meals"
on the probability that a school will hold classes year round:

```{r, eval = TRUE}
m.sm1.diff <- scompare(m.sm1, "meals")
summary(m.sm1.diff)
```

Generate a second set of fitted values and a plot:

```{r}
library(ggplot2)

ggplot(m.sm1.diff, aes(x = .smargin_qi)) +
    geom_density(fill = "blue", alpha = 0.25)
```

### Example 2: User has Details about Complex Survey Design (but not sample weights)

Suppose that the survey house that provided the dataset excluded
probability weights but made other details about the survey design
available. We can still estimate a model without probability weights
that takes instead variables that identify each the stratum and/or
cluster from which each observation was selected and the size of the
finite sample from which each observation was selected.

```{r, eval = TRUE}
apiclus.design <- svydesign(ids = ~1, strata = ~stype, fpc = ~fpc, data = apistrat)

m2 <- svyglm(yr.rnd ~ meals + mobility,
             design = apiclus.design,
             family = quasibinomial())

summary(m2)
```

The coefficient estimates from this model are identical to
point estimates in the previous example, but the standard errors
are smaller.

```{r}
m.sm2 <- smargins(m2, meals = quantile(apistrat$meals, c(0.2, 0.8)))
summary(m.sm2)
```
