---
title: "AMEs for Regression with Survey Weights"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ame-survey-glm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
    stop_on_error = 2L
)
knitr::opts_chunk$set(
    fig.height = 11,
    fig.width = 7
)

options(cite = FALSE)
```
---

Logit Regression for Dichotomous Dependent Variables with Survey Weights with
`logit.survey`.

Use logit regression to model binary dependent variables specified as a
function of a set of explanatory variables.

Examples
------

```{r, eval = TRUE, echo = FALSE}
rm(list=ls(pattern="\\.out"))
suppressWarnings(suppressMessages(library(Zelig)))
set.seed(1234)
```

### Example 1: User has Existing Sample Weights

Our example dataset comes from the survey package:

```{r, eval = TRUE}
data(api, package = "survey")
```

In this example, we will estimate a model using
the percentages of students who receive subsidized
lunch and the percentage who are new to a school
to predict whether each California public school
attends classes year round.  We first make a numeric
version of the variable in the example dataset, which
you may not need to do in another dataset.

```{r, eval = TRUE}
library(survey)

apistrat.design <- svydesign(ids = ~1, weights = ~pw, data = apistrat)

m1 <- svyglm(yr.rnd ~ meals + mobility,
             design = apistrat.design,
             family = quasibinomial())

summary(m1)
```

Set explanatory variables to their observed values, and set
a high (80th percentile) and low (20th percentile) value for "meals,"
the percentage of students who receive subsidized meals:

```{r, eval = TRUE}
library(smargins)

m.sm1 <- smargins(m1, at = list(meals = quantile(apistrat$meals, c(0.2, 0.8))), n = 10000)
summary(m.sm1)
```

Generate first differences for the effect of high versus low "meals"
on the probability that a school will hold classes year round:

```{r, eval = TRUE}
m.sm1.diff <- scompare(m.sm1, "meals")
summary(m.sm1.diff)
```

Generate a second set of fitted values and a plot:

```{r}
library(ggplot2)

ggplot(m.sm1.diff, aes(x = .smargin_qi)) +
    geom_density(fill = "blue", alpha = 0.25)
```

### Example 2: User has Details about Complex Survey Design (but not sample weights)

Suppose that the survey house that provided the dataset excluded
probability weights but made other details about the survey design
available. We can still estimate a model without probability weights
that takes instead variables that identify each the stratum and/or
cluster from which each observation was selected and the size of the
finite sample from which each observation was selected.

```{r, eval = TRUE}
apiclus.design <- svydesign(ids = ~1, strata = ~stype, fpc = ~fpc, data = apistrat)

m2 <- svyglm(yr.rnd ~ meals + mobility,
             design = apiclus.design,
             family = quasibinomial())

summary(m2)
```

The coefficient estimates from this model are identical to
point estimates in the previous example, but the standard errors
are smaller.

```{r}
m.sm2 <- smargins(m2, at = list(meals = quantile(apistrat$meals, c(0.2, 0.8))))
summary(m.sm2)
```

Model
------

Let $Y_i$ be the binary dependent variable for observation
$i$ which takes the value of either 0 or 1.

-  The *stochastic component* is given by


$$
    \begin{aligned}
        Y_i &\sim& \textrm{Bernoulli}(y_i \mid \pi_i) \\
          &=& \pi_i^{y_i} (1-\pi_i)^{1-y_i}\end{aligned}
$$
   where $\pi_i=\Pr(Y_i=1)$.

-  The *systematic component* is given by:


$$
    \pi_i \; = \; \frac{1}{1 + \exp(-x_i \beta)}.
$$

   where $x_i$ is the vector of $k$ explanatory variables
   for observation $i$ and $\beta$ is the vector of
   coefficients.

Quantities of Interest
------

-  The expected values (`qi$ev`) for the logit model are simulations of
   the predicted probability of a success:


$$
    E(Y) =
        \pi_i= \frac{1}{1 + \exp(-x_i \beta)},
$$

   given draws of $\beta$ from its sampling distribution.

-  The predicted values (`qi$pr`) are draws from the Binomial distribution
   with mean equal to the simulated expected value $\pi_i$.

-  The first difference (qi$fd) for the logit model is defined as


$$
    \textrm{FD} = \Pr(Y = 1 \mid x_1) - \Pr(Y = 1 \mid x).
$$

-  The risk ratio (qi$rr) is defined as


$$
    \textrm{RR} = \Pr(Y = 1 \mid x_1) \ / \ \Pr(Y = 1 \mid x).
$$

-  In conditional prediction models, the average expected treatment
   effect (att.ev) for the treatment group is


$$
    \frac{1}{\sum_{i=1}^n t_i}\sum_{i:t_i=1}^n \left\{ Y_i(t_i=1) -
        E[Y_i(t_i=0)] \right\},
$$

   where $t_i$ is a binary explanatory variable defining the
   treatment ($t_i=1$) and control ($t_i=0$) groups.
   Variation in the simulations are due to uncertainty in simulating
   $E[Y_i(t_i=0)]$, the counterfactual expected value of
   $Y_i$ for observations in the treatment group, under the
   assumption that everything stays the same except that the treatment
   indicator is switched to $t_i=0$.

-  In conditional prediction models, the average predicted treatment
   effect (att.pr) for the treatment group is


$$
    \frac{1}{\sum_{i=1}^n t_i}\sum_{i:t_i=1}^n \left\{ Y_i(t_i=1) -
        \widehat{Y_i(t_i=0)}\right\},
$$

   where $t_i$ is a binary explanatory variable defining the
   treatment ($t_i=1$) and control ($t_i=0$) groups.
   Variation in the simulations are due to uncertainty in simulating
   $\widehat{Y_i(t_i=0)}$, the counterfactual predicted value of
   $Y_i$ for observations in the treatment group, under the
   assumption that everything stays the same except that the treatment
   indicator is switched to $t_i=0$.

