---
title: "Transforming Covariates"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Transforming Covariates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
        stop_on_error = 2L
)
```

## Supported transformations

For convenience, you may wish to transform one or more of your covariates within the model estimation call. For example, imagine we want to natural log transform the variable `dist` in a linear regression:

```{r, message=FALSE}
cars <- transform(cars, dist.log = log(dist))
m.log <- lm(speed ~ log(dist), data = cars)
m.log2 <- lm(speed ~ dist.log, data = cars)
```

Then we want to find quantities of interest when the `dist` variable is 26 to
56 (the first to third quartile):

```{r}
library(smargins)

summary(smargins(m.log, at = list(dist = c(26, 56))))
```

We could also estimate the model with `dist` as a polynomial. For example:

```{r message=FALSE}
# Find range of polynomial values

m2 <- lm(speed ~ poly(dist, 2), data = cars)
summary(smargins(m2, at = list(dist = with(cars, seq(min(dist), max(dist), 10)))))
```

Splines and other transformations should generally work as expected.

```{r, message=FALSE}
library(splines)

m3 <- lm(speed ~ bs(dist, df = 4), data = cars)
summary(smargins(m3, at = list(dist = with(cars, seq(min(dist), max(dist), 10)))))
```
