---
title: "Expected Values for Tobit Models"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AMEs for Tobit Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
    stop_on_error = 2L
)
knitr::opts_chunk$set(
    fig.height = 11,
    fig.width = 7
)

options(cite = FALSE)
```
---


Examples
------

```{r, eval = TRUE, echo = FALSE}
rm(list=ls(pattern="\\.out"))
suppressWarnings(suppressMessages(library(Zelig)))
set.seed(1234)
```

### Basic Example

Attaching the sample dataset:

```{r, eval = TRUE}
library(survival)
data(tobin)
```

Estimating linear regression using `tobit`:

```{r, eval = TRUE}
## consider these two models:
m1 <- survreg(Surv(durable, durable>0, type='left') ~ age + quant,
              data=tobin, dist='gaussian')
```

Summarize estimated paramters:

```{r, eval = TRUE}
summary(m1)
```

Setting values for the explanatory variables to their sample averages
and simulating quantity of interest.

```{r, eval = TRUE}
library(smargins)

m.sm <- smargins(m1, quant = seq(210, 280, 10))

summary(m.sm)

library(ggplot2)

ggplot(summary(m.sm), aes(x = quant, y = mean)) +
    geom_smooth(aes(ymin = lower_2.5, ymax = upper_97.5),
                stat = "identity")
```

### Simulating First Differences

Set explanatory variables to their default(mean/mode) values, with
high (80th percentile) and low (20th percentile) liquidity ratio
(`quant`):

```{r, eval = TRUE}
m.sm2 <- smargins(m1, quant = quantile(tobin$quant, prob = c(0.2, 0.8)))

summary(m.sm2)
```

Estimating the first difference for the effect of high versus low
liquidity ratio on duration(\ `durable`):

```{r, eval = TRUE}
summary(scompare(m.sm2, "quant"))
ggplot(scompare(m.sm2, "quant"), aes(x = .smargin_qi)) +
    geom_density(fill = "blue", alpha = 0.25)
```

Model
------

-  Let $Y_i^*$ be a latent dependent variable which is distributed
   with *stochastic* component


$$
    \begin{aligned}
        Y_i^* & \sim & \textrm{Normal}(\mu_i, \sigma^2) \\\end{aligned}
$$

   where $\mu_i$ is a vector means and $\sigma^2$ is a
   scalar variance parameter. $Y_i^*$ is not directly observed,
   however. Rather we observed $Y_i$ which is defined as:


$$
    Y_i = \left\{
        \begin{array}{lcl}
      Y_i^*  &\textrm{if} & c <Y_i^* \\
      c    &\textrm{if} & c \ge Y_i^*
      \end{array}\right.
$$

   where $c$ is the lower bound below which $Y_i^*$ is
   censored.

-  The *systematic component* is given by


$$
    \begin{aligned}
        \mu_{i} &=& x_{i} \beta,\end{aligned}
$$

   where $x_{i}$ is the vector of $k$ explanatory variables
   for observation $i$ and $\beta$ is the vector of
   coefficients.

Quantities of Interest
------

-  The expected values (`qi$ev`) for the tobit regression model are
   the same as the expected value of $Y*$:


$$
    E(Y^* | X) = \mu_{i} = x_{i} \beta
$$

-  The first difference (`qi$fd`) for the tobit regression model is
   defined as


$$
    \begin{aligned}
        \text{FD}=E(Y^* \mid x_{1}) - E(Y^* \mid x).\end{aligned}
$$

-  In conditional prediction models, the average expected treatment
   effect (`qi$att.ev`) for the treatment group is


$$
    \begin{aligned}
        \frac{1}{\sum t_{i}}\sum_{i:t_{i}=1}[E[Y^*_{i}(t_{i}=1)]-E[Y^*_{i}(t_{i}=0)]],\end{aligned}
$$

   where $t_{i}$ is a binary explanatory variable defining the
   treatment ($t_{i}=1$) and control ($t_{i}=0$) groups.
